--- 
title: "TMT.KOR Book of Data"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
link-citations: yes
github-repo: rstudio/bookdown-demo
---

# Overview {-}

This bookdown project contains raw data, data analyses, and code to generate data visualizations for the paper [**A single exposure to the predator odor 2,4,5-trimethylthiazoline causes long-lasting affective behavioral changes in female mice: Modulation by kappa opioid receptor signaling**](https://www.sciencedirect.com/science/article/pii/S0091305724001163#f0010)

- Raw data and code to generate the figure panels are available on our github.

- Code to generate the figures and statistical analyses was written by **Jennet Baumbach**.

- Any questions about these data should be directed to the corresponding author: **Loren Martin**, Ph.D lj.martin@utoronto.ca

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup_GP_TMT_FRZ, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(scipen=999)
```
